Manuscript

### 2023-05-26 Manuscript1.Rmd
updates

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(tidyverse, osfr, lmerTest, MuMIn, DHARMa, here, cmdstanr, tidybayes, bayesplot, posterior,future,furrr, patchwork, R.utils, brms, extraDistr)

@@

plot_spacer()+kalmanplot+rwplot+wbplot+plot_layout(design = layout)

@@

@@

<!-- ```{r fitting to both sessions to hierachiacal RW} -->

<!-- data1 = list(nsubs = length(unique(data$id)), -->
<!--             ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])), -->
<!--             sessions = 2, -->
<!--             pred = get_3darray(data,variable = "pred"), -->
<!--             u = get_3darray(data,variable = "u") -->
<!--             ) -->

<!-- rw_fit_ses1 <- mod$sample( -->
<!--       data = data1, -->
<!--       chains = 4, -->
<!--       parallel_chains = 4, -->
<!--       refresh = 100, -->
<!--       adapt_delta = 0.90, -->
<!--       max_treedepth = 12 -->
<!--     ) -->

<!-- sum = rw_fit_ses1$summary(variables = c("alpha", "mu_alpha","sd_alpha","mu_mu_alpha","sd_sd_alpha","mu_sd_alpha","sd_mu_alpha")) -->
<!-- ``` -->

<!-- ```{r, fitting to real data tester hierachical RW sessions1} -->
<!-- df= read.csv(here::here("data_TPL_AC.csv")) %>% -->
<!--   rename_all(tolower) %>% -->
<!--   filter(trial != 0) %>% -->
<!--   rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% -->
<!--   mutate_all(replace_na, 0) -->

<!-- df = df %>% filter(session == 1) -->

<!-- rw_fit_ses1 <- mod$sample( -->
<!--       data = data2, -->
<!--       chains = 4, -->
<!--       parallel_chains = 4, -->
<!--       refresh = 100, -->
<!--       adapt_delta = 0.90, -->
<!--       max_treedepth = 12 -->
<!--     ) -->

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(tidyverse, osfr, lmerTest, MuMIn, DHARMa, here, cmdstanr, tidybayes, bayesplot, posterior,future,furrr, patchwork, R.utils, brms, extraDistr,cowplot)

@@

trial_struc = ggdraw() +
  draw_image(magick::image_read(here::here("figures", "main-experiment.PNG")), scale = 1.5)

trial_struc+kalmanplot+rwplot+wbplot+plot_layout(design = layout)+plot_annotation(tag_levels = 'A')

RW_logistic = RW_logistic_vis(dd)
```

@@

plot_parameterrecovery(kalman_pp, div = T, subs = 5)

@@

```{r fitting to both sessions to hierachiacal RW}

#source(here::here("stan_functions.R"))
#fitting hierachically
data = df %>% mutate(percept = percept/100)

data1 = list(nsubs = length(unique(data$id)),
            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
            sessions = 2,
            pred = get_3darray(data,variable = "pred"),
            u = get_3darray(data,variable = "u")
            )

mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier.stan"))

rw_fit_ses1 <- mod$sample(
      data = data1,
      chains = 4,
      parallel_chains = 4,
      refresh = 100,
      adapt_delta = 0.90,
      max_treedepth = 12
    )

sum = rw_fit_ses1$summary(variables = c("alpha", "mu_alpha","sd_alpha","mu_mu_alpha","sd_sd_alpha","mu_sd_alpha","sd_mu_alpha"))
```

```{r, fitting to real data tester hierachical RW sessions1}

#source(here::here("stan_functions.R"))
#fitting hierachically
data = df %>% mutate(percept = percept/100)

data2 = list(nsubs = length(unique(data$id)),
            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)),
            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
            )

mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier_complete.stan"))

rw_fit_ses1 <- mod$sample(
      data = data2,
      chains = 4,
      parallel_chains = 4,
      refresh = 100,
      adapt_delta = 0.90,
      max_treedepth = 12
    )

sum1 = rw_fit_ses1$summary()
```

```{r, fitting to real data tester hierachical RW sessions2}

#source(here::here("stan_functions.R"))
#fitting hierachically
data = df %>% mutate(percept = percept/100)

data2 = list(nsubs = length(unique(data$id)),
            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)),
            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
            )

mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier_complete.stan"))

rw_fit_ses2 <- mod$sample(
      data = data2,
      chains = 4,
      parallel_chains = 4,
      refresh = 100,
      adapt_delta = 0.90,
      max_treedepth = 12
    )

sum2 = rw_fit_ses2$summary()

get_corplot(rw_fit_ses1,rw_fit_ses2, "b2_b")
```

```{r}

data1 = list(nsubs = length(unique(data$id)),
            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
            sesions = length(unique(data$session)),
            percept = get_3darray(data,variable = "percept"),
            pred = get_3darray(data,variable = "pred"),
            percept_bin = get_3darray(data,variable = "percept_bin"),
            stim = get_3darray(data,variable = "stim"),
            cues = get_3darray(data,variable = "cue"),
            u = get_3darray(data,variable = "u")
            )

mod = cmdstan_model(here::here("Stan","fitting both sessions","rw_vs_rw_hier_complete_both_sessions.stan"))

fit <- mod$sample(
  data = data1,
  chains = 4,
  parallel_chains = 4,
  refresh = 10,
  adapt_delta = 0.90,
  max_treedepth = 12
)

```{r}
mu_alpha = 0.3
kappa_alpha = 30

mu_b0 = -5
sd_b0 = 1

mu_b1 = -1
sd_b1 = 1

mu_b2 = 1.3
sd_b2 = 1.3

mu_b0_b = -5
sd_b0_b = 2

mu_b1_b = 0.5
sd_b1_b = 0.5

mu_b2_b = 0.5
sd_b2_b = 0.5

sd_percept_precision = 0.5

parameters = expand.grid(mu_alpha = mu_alpha,
                         kappa_alpha = kappa_alpha,
                         mu_b0 = mu_b0,
                         sd_b0 = sd_b0,
                         mu_b1 = mu_b1,
                         sd_b1 = sd_b1,
                         mu_b2 = mu_b2,
                         sd_b2 = sd_b2,
                         mu_b0_b = mu_b0_b,
                         sd_b0_b = sd_b0_b,
                         mu_b1_b = mu_b1_b,
                         sd_b1_b = sd_b1_b,
                         mu_b2_b = mu_b2_b,
                         sd_b2_b = sd_b2_b,
                         sd_percept_precision = sd_percept_precision,
                         nsubs = nsubs)

df = hier_rw_logistic(parameters)

data = df[[1]]

data2 = list(nsubs = length(unique(data$id)),
            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)),
            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
            )

hier = df[[2]]
df = df[[1]]

mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier_complete.stan"))

fit <- mod$sample(
      data = data2,
      chains = 4,
      parallel_chains = 4,
      refresh = 100,
      adapt_delta = 0.90,
      max_treedepth = 12
    )

hier_parameters = c("mu_b0","mu_b1","mu_b2","sd_b0","sd_b1","sd_b2","mu_b0_b","mu_b1_b","mu_b2_b","sd_b0_b","sd_b1_b","sd_b2_b","kappa_alpha","mu_alpha","sd_percept_precision")

sub_parameters = c("b0","b1","b2","b0_b","b1_b","b2_b","alpha","percept_precision")

list(hier = data.frame(fit$summary(hier_parameters),
                                  reals = hier %>% dplyr::select(all_of(hier_parameters)) %>% pivot_longer(everything()) %>% rename(reals = value),
                                  div = sum(fit$diagnostic_summary()$num_divergent),index = index),
                sub = data.frame(fit$summary(sub_parameters) %>% arrange(variable),
                                 reals = df %>% filter(trial == 1) %>% mutate(ids = 1:nrow(.)) %>% dplyr::select(all_of(sub_parameters),ids) %>% 
                                 pivot_longer(cols = -ids) %>% rename(reals =value) %>% mutate(names = paste0(name,"[",ids,"]")) %>% arrange(names) %>% select(names,reals),
                                 div = sum(fit$diagnostic_summary()$num_divergent),index = index))

#sum = fit$summary()

```{r}
mu_alpha = seq(0.1,0.5, length.out = 5)
kappa_alpha = seq(10,100, length.out = 2)

mu_b0 = -1.5
sd_b0 = 0.5

mu_b1 = 2
sd_b1 = 0.5

mu_b2 = 0.1
sd_b2 = 0.5

mu_b0_b = -4
sd_b0_b = 0.5

mu_b1_b = 7
sd_b1_b = 0.5

mu_b2_b = 0.7
sd_b2_b = 0.5

sd_percept_precision = 0.8

parameters = expand.grid(mu_alpha = mu_alpha,
                         kappa_alpha = kappa_alpha,
                         mu_b0 = mu_b0,
                         sd_b0 = sd_b0,
                         mu_b1 = mu_b1,
                         sd_b1 = sd_b1,
                         mu_b2 = mu_b2,
                         sd_b2 = sd_b2,
                         mu_b0_b = mu_b0_b,
                         sd_b0_b = sd_b0_b,
                         mu_b1_b = mu_b1_b,
                         sd_b1_b = sd_b1_b,
                         mu_b2_b = mu_b2_b,
                         sd_b2_b = sd_b2_b,
                         sd_percept_precision = sd_percept_precision,
                         nsubs = nsubs)

rw_pp = furrr::future_map(data_list, ~parameter_recovery_logistic_rw(.x), .progress = TRUE, .options = furrr_options(seed = 123))
